Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-07 SupportingInformation.Rmd
asym_sens : table with model sel and npa stat for all b and g1,g2 added in suppmat

```{r read_tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")

@@

```{r tab_stat_npa_asym_1,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[1]])
knitr::kable(temp, booktabs = T, 
             format = "latex",linesep = "",escape=F,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_1}")
```

```{r tab_stat_npa_asym_2,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[2]])
knitr::kable(temp, booktabs = T, 
             format = "latex",linesep = "",escape=F,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_2}")
```

>>>>

```{r read_tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
#tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")

@@

```{r tab_stat_npa_asym,echo=F,results="markup"}
library(kableExtra)

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}

knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Results for tests of whether asymmetry of tail dependence was significant
                              compared to a normal-copula null hypothesis.",
             caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more)
                      than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ 
                      or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail         
                      dependence.\\label{tab_stat_npa_asym}")%>%
             kable_styling()%>%
             group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
             group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
             group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
             group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
             group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
             group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
             group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
             group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```
